Model of lens candidates from Space Warps CFHTLS

### 2016-07-26 paper2.tex
small extension
notes
edits

\title[Short title, max. 45 characters]{Model of lens candidates from
  Space Warps CFHTLS}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor

@@

Section~\ref{sec:spl} summarises the SpaghettiLens system and
discusses its ongoing development. A SpaghettiLens model consists of a
statistical ensemble of free-form maps of the sky-projected mass
distribution responsible for lensing.  Each lens candidates in
practice gets modelled several times in a collaborative refinement
process\footnote{See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
  the model tree.}  In this paper we report the most recent model for
each lens, as representing a consensus among modellers, as to the best
that could be achieved with the available data and software.
Photometric lens redshifts are used; source redshifts are set to
$z=2$.  The models can, however, be trivially rescaled to use better
redshift values, as and when they become available.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.  The first two of those are
taken up in Section~\ref{sec:spl}, along with a further idea. In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 25 innermost mass tiles solves the problem completely, but increases
the number of mass tiles by 40% and thus at least triples the
% in practice, it's more x4 - x5! 87/22, 86/21, 85/16
computation time.  The main modelling work in this paper was, however,
done before the experiments with smaller mass tiles was complete.
Hence the results in this paper use the intermediate option
(corresponding to the middle panel in Figure~\figref{subsampling}).
As the results in this paper mainly concern the enclosed mass in the
outer regions, the remaining shallowness in the central region should
be inconsequential.

@@

@@

Based on \cite{2003MNRAS.344.1000B} models.\todo{Needs text.}

@@

\begin{figure}
%  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
  \caption{Model results for SW05 (J143454.4+522850).  See text in
    Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}

@@

Table~\ref{tab:models}

>>>>

\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
  Space Warps CFHTLS}

@@

Section~\ref{sec:spl} summarises the SpaghettiLens system and
discusses its ongoing development. A SpaghettiLens model consists of a
statistical ensemble of free-form maps of the sky-projected mass
distribution responsible for lensing.  Each lens candidates in
practice gets modelled several times in a collaborative refinement
process\footnote{See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
  the model tree.}  In this paper we report the most recent model for
each lens, as representing a consensus among modellers, as to the best
that could be achieved with the available data and software.
Photometric lens redshifts are used; source redshifts are set to
$z=2$ unless an unambiguous photometric redshift is available.
The models can, however, be trivially rescaled to use better
redshift values, as and when they become available.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.  The first two of those are
taken up in Section~\ref{sec:spl}, along with a further idea. In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 25 innermost mass tiles solves the problem completely, but
increases the number of mass tiles by 40\% and significantly increases
the computational time.
% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
% runtimes from logfiles: 87/22, 86/21, 85/16
The main modelling work in this paper was, however, done before the
experiments with smaller mass tiles was complete.  Some of the models
presented in this paper apply the intermediate option (corresponding
to the middle panel in Figure~\figref{subsampling}) while others use
the old system.  The results in this paper, however, mainly concern
the enclosed mass in the outer regions, so shallowness in the central
region should be inconsequential.

@@

\begin{figure}
  \caption{}
  \label{fig:parameter}
\end{figure}

@@

Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
  stellar-population models.}

@@

\begin{figure}
  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
  \caption{Model results for SW05 (J143454.4+522850).  See text in
    Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}

@@

Table~\ref{tab:models} shows a summary of the analysis for many candidates.
Missing rows are due to photometry data not available.
